Reanalysis Step 5: Outcome Analysis with Full Four-Treatment Interaction (Monotherapy Only)

### 2025-09-04 reanalysis-5-outcome_analysis-full_interaction.qmd
full

## Check Cell Sizes for Full Interaction

```{r check-cells}
# Check cell sizes for the three-way interaction
first_data <- imputed_datasets[[1]]
cell_counts <- first_data |>
  count(ever_lapse_binary, dr_severity, treatment_type) |>
  arrange(n)

# Identify problematic cells
small_cells <- cell_counts |> filter(n < MIN_N_PER_CELL)

if (nrow(small_cells) > 0) {
  log_message(paste0("WARNING: ", nrow(small_cells), 
                    " cells have fewer than ", MIN_N_PER_CELL, " observations"))

  print(kable(small_cells, 
              caption = paste("Cells with < ", MIN_N_PER_CELL, " observations")))

  # Decide whether to proceed
  if (nrow(small_cells) > length(unique(first_data$treatment_type))) {
    warning("Many small cells detected. Model may be unstable.")
    # Could stop here or collapse categories
  }
}

# Display full interaction table
interaction_table <- cell_counts |>
  pivot_wider(
    names_from = treatment_type,
    values_from = n,
    values_fill = 0
  ) |>
  arrange(ever_lapse_binary, dr_severity)

kable(interaction_table,
      caption = "Cell sizes for Lapse × DR Severity × Treatment Type (4 levels)")
```

>>>>

## Average Cell Sizes Across Imputations

```{r average-cell-counts}
# Compute cell counts for each imputation
all_cell_counts <- list()

for (i in 1:n_imputations) {
  cell_counts <- imputed_datasets[[i]] |>
    count(ever_lapse_binary, dr_severity, treatment_type) |>
    mutate(imputation = i)

  all_cell_counts[[i]] <- cell_counts
}

# Combine all imputations
combined_counts <- bind_rows(all_cell_counts)

# Calculate average counts across imputations
average_counts <- combined_counts |>
  group_by(ever_lapse_binary, dr_severity, treatment_type) |>
  summarise(
    mean_n = mean(n),
    sd_n = sd(n),
    min_n = min(n),
    max_n = max(n),
    .groups = "drop"
  ) |>
  arrange(ever_lapse_binary, dr_severity, treatment_type)

# Display average cell counts in wide format
average_table <- average_counts |>
  select(ever_lapse_binary, dr_severity, treatment_type, mean_n) |>
  pivot_wider(
    names_from = treatment_type,
    values_from = mean_n,
    values_fill = 0
  ) |>
  arrange(ever_lapse_binary, dr_severity)

kable(average_table,
      caption = paste0("Average cell sizes across ", n_imputations, " imputations"),
      digits = 1,
      col.names = c("Lapse", "DR Severity", names(average_table)[-(1:2)]))

# Identify small cells (averaged across imputations)
small_cells <- average_counts |> 
  filter(mean_n < MIN_N_PER_CELL)

if (nrow(small_cells) > 0) {
  log_message(paste0("WARNING: ", nrow(small_cells), 
                    " cells have average count < ", MIN_N_PER_CELL))

  kable(small_cells |> 
        select(ever_lapse_binary, dr_severity, treatment_type, 
               mean_n, min_n, max_n) |>
        arrange(mean_n),
        caption = paste0("Cells with average count < ", MIN_N_PER_CELL),
        digits = 1,
        col.names = c("Lapse", "DR Severity", "Treatment", "Mean N", "Min N", "Max N"))
}

# Summary statistics
total_cells <- nrow(average_counts)
sparse_cells <- sum(average_counts$mean_n < 30)
very_sparse_cells <- sum(average_counts$mean_n < 10)

cat("\n### Cell Count Summary\n")
cat("- Total cells in 3-way interaction:", total_cells, "\n")
cat("- Cells with average n < 30:", sparse_cells, 
    "(", round(100*sparse_cells/total_cells, 1), "%)\n")
cat("- Cells with average n < 10:", very_sparse_cells,
    "(", round(100*very_sparse_cells/total_cells, 1), "%)\n")
cat("- Smallest average cell size:", round(min(average_counts$mean_n), 1), "\n")
cat("- Largest average cell size:", round(max(average_counts$mean_n), 1), "\n")
```
